QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 format.tex
rename problem types to something more familiar (issue #4)
I'll update the qplib instances on the up-to-be qplib website accordingly.

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\texttt{#1}}
\begin{description}
\item [{[1]}]
%\todo[inline]{\small Fabio and Emiliano: we think that, if possible, we should follow the classification proposed in Section 2.}

The problem type is represented by a character string as one of the following:
\begin{description}
\item For continuous problems (i.e., all variables are continuous):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [LP]      a linear program,
\item [LPQC]    a linear program with quadratic constraints,
\item [BQP]     a bound-constrained quadratic program,
\item [QP]      a quadratic program, and
\item [QPQC]    a quadratic program with quadratic constraints.
\end{description}
\item For integer problems (i.e., all variables are integer valued):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [ILP]     an integer linear program,
\item [ILPQC]   an integer linear program with quadratic constraints,
\item [IBQP]    an integer bound-constrained quadratic program,
\item [IQP]     an integer quadratic program, and
\item [IQPQC]   an integer quadratic program with quadratic constraints.
\end{description}
\item For mixed-integer problems (i.e., there is a mix of continuous and
integer variables):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [MILP]    a mixed-integer linear program,
\item [MILPQC]  a mixed-integer linear program with quadratic constraints,
\item [MIBQP]   a mixed-integer bound-constrained quadratic program,
\item [MIQP]    a mixed-integer quadratic program, and
\item [MIQPQC]  a mixed-integer quadratic program with quadratic constraints.
\end{description}
\end{description}

\item [{[2]}]
for bound-constrained QPs, these sections are omitted.
\item [{[3]}]
for linear program with quadratic constraints, this section is omitted.
\item [{[4]}]
for problems without quadratic constraints, this section is omitted.
\item [{[5]}]
for purely-continuous or purely-integer problems, this section is omitted.
\end{description}

>>>>

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\texttt{#1}}
\begin{description}
\item [{[1]}]
%\todo[inline]{\small Fabio and Emiliano: we think that, if possible, we should follow the classification proposed in Section 2.}
The problem type is represented by a character string as one of the following:
\begin{description}
\item For continuous problems (i.e., all variables are continuous):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [LP]   a problem with linear objective and linear constraints,
\item [QCP]  a problem with linear objective and linear and quadratic constraints,
\item [BQP]  a problem with quadratic objective and variable bounds,
\item [QP]   a problem with quadratic objective and linear constraints, and
\item [QCQP] a problem with quadratic objective and linear and quadratic constraints.
\end{description}

\item For integer problems (i.e., all variables are integer valued):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [ILP]   an LP plus integer requirement for all variables,
\item [IQCP]  an QCP plus integer requirement for all variables,
\item [IBQP]  an BQP plus integer requirement for all variables,
\item [IQP]   an QP plus integer requirement for all variables, and
\item [IQCQP] an QCQP plus integer requirement for all variables.
\end{description}

\item For mixed-integer problems (i.e., there is a mix of continuous and
integer variables):
\begin{description}[leftmargin=!,labelwidth=\widthof{\texttt{SMILQPC}}]
\item [MILP]   an LP plus integer requirement for some variables,
\item [MIQCP]  an QCP plus integer requirement for some variables,
\item [MIBQP]  an BQP plus integer requirement for some variables,
\item [MIQP]   an QP plus integer requirement for some variables, and
\item [MIQCQP] an QCQP plus integer requirement for some variables.
\end{description}
\end{description}

\item [{[2]}]
for BQPs, IBQPs, and MIBQPs, these sections are omitted.
\item [{[3]}]
for LPs, QCPs, ILPs, IQCPs, MILPs, MIQCPs, this section is omitted.
\item [{[4]}]
for LPs, BQPs, QPs, ILPs, IBQPs, IBQPs, MILPs, MIBQPs, MIBQPs, this section is omitted.
\item [{[5]}]
for purely-continuous or purely-integer problems, this section is omitted.
\end{description}
